CDSR Human Data/Modelling Paper

### 2013-09-12 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex

Consider the following regions (shown in Figure \ref{fig:examples}): the front of a classroom, safety in a military engagement, or the geographical feature of a bottleneck.  To determine these regions, one must identify the physical boundaries (e.g., walls, bodies of water), the objects within the environment, their orientation and their functional use (e.g., desks oriented toward a whiteboard), and other agents' intentions and capabilities (e.g., enemy tanks can move and have a range of attack).  Furthermore, these regions exist at different levels of spatial resolution.  Consider a neighborhood in a city, whose boundaries expand and contract over time with changes to the surrounding residents and businesses.

@@

\subsection{Research Questions, Design and Stimuli}

We developed the study described below in order to examine the following questions about CDSRs:
\begin{enumerate}
	\item Given a particular situation how well do people agree on the location and extent of a named CDSR?
	\item Does the orientation and location of objects (with relevant functional semantics) in a given situation effect the location and extent of a named CDSR?
\end{enumerate}

Both of these research questions address the fundamental claim that CDSRs are contextually defined. Question 1 addresses this claim by examining variation in CDSR placement within different situtations. In a situation exhibiting clear contextual clues (e.g. determining a safe zone in a battle situation where all information is known and battle formations are well-defined) one would expect high agreement in human identification of the CDSR. In a less well-defined context, one might expect little to no agreement between human communicators.  Research question 2 addresses the contextual nature of CDSRs in terms of whether or not the variation in the location and extent of a CDSR systematically follow the variations  in the given context.

@@

To examine these questions, we developed two experimental tasks:
\begin{itemize}
	\item{Task 1:} subjects were presented with a visual representation of a spatial scene plus a linguistic description containing a CDSR and were tasked with drawing a polygon on the visual stimuli such that it defined the location and extent of the CDSR in the scene (or stated there was no such region).
	\item{Task 2:} subjects were presented with a visual representation of a spatial scene with a marked location and an accompanying spatial description and were asked to rate how well the marked location fit with their understanding of the CDSR on a five point likert scale.
\end{itemize}

@@

% kate: vocabulary clarification: situation vs. context??

@@

The classroom stimuli consisted of pairs of floor plans and photos of classrooms with different chair configurations. For example, Figure \ref{fig:classroom-a} is a floor plan of a classroom where the chairs have been arranged in a circle and Figure \ref{fig:classroom-b} is the accompanying photo of this classroom. We developed four different classroom stimuli each with a different layout of chairs: a circular chair layout, a U shaped layout (Figure \ref{fig:classroom-c} and Figure \ref{fig:classroom-d}), a typical row-based layout with the first row of chairs close to the expected front of the room (Figure \ref{fig:classroom-e}), and the same arrangement with the front row of chairs further away from the expected front of the room (Figure \ref{fig:classroom-f})\footnote{In the interest of saving space we do not show all the classroom photo stimuli}. To control for left-right bias effects, two versions of the U shaped layout, close rows layout and far rows layout were created by horizontally flipping the layouts. Consequently, there were 7 classroom stimuli (circle, U $\times$ 2, close $\times$ 2, far $\times$ 2). In designing these stimuli we deliberately chose some layouts that were very common or close variations on standard layouts - e.g., Figures \ref{fig:classroom-e} and \ref{fig:classroom-f} - and others were more novel - Figure \ref{fig:classroom-a} and \ref{fig:classroom-c}. By varying the typicality of the layouts we hoped to get some variation across the between subject agreement on a per stimuli basis, for example we expected to get a higher between subject agreement for the stimuli that were more common. This would provide insight into research question 1, in particular it would point to the effect of typicality on the semantics of contextually defined spatial regions. Also, because the typicality of the scenes was varied by adjusting the location and orientation of objects in the scenes, a variation in agreement across the stimuli would provide evidence that the orientation and location of objects do effect the location and extent of spatial regions.

@@

The geographical map stimuli, Figures \ref{fig:bottleneck-a} and \ref{fig:bottleneck-b}, differed in the width of the bottleneck region. We hoped this variation would result in a variation in the size of the polygons for these different visual contexts. Finally, the military engagement stimuli, Figures \ref{fig:tanks-a}, \ref{fig:tanks-b}, \ref{fig:turrets-a}, \ref{fig:tanks-b} varied the functionality of the objects in the scene (tanks that could move versus fixed turret emplacements), the location of the objects in the scenes (were the tanks close to the bottom of the image or near the top), and the number and layout of the objects (the number and layout of the turrets were varied). Again, a variation across the between subject agreement on the different stimuli would provide evidence for the impact of object location and orientation on spatial semantics.

@@

\subsection{Task 1 - Results}
We use two methods to analyze the results of region drawing task.  First, we use interannotator agreement for two reasons: (1) if there is fair to good overall agreement, this is evidence that people change the regions they produce based systematically with context, (2) we expect less agreement in ambiguous situations (e.g., the circle (a) and U-shaped (c) of desk arrangements as well as the turret + 1 (l) military engagement configuration).  Second, we use the extent points of the regions to assess changes between trials.  That is, as the desks are moved back from stimuli (e) to (f), we expect the maximum x-coordinate of the region to increase.

@@

We use \textbf{Cohen's kappa coefficient}, $\kappa$, to measure the agreement between two regions as follows.  We generated a set of 47,000 test points that were uniformly distributed across each stimuli and used each subject's polygon to classify the test points as being inside or outside the polygon. After classifying the test points for each subject we then computed an average pairwise kappa score for each subject with all the other subjects on a per stimuli basis. In this calculation if either of the subjects in a pair entered a no region response for a particular stimuli a $\kappa$ value of 0 was used.  $\kappa$ ranges from 0 indicating no agreement beyond chance to 1 indicating complete agreement.

@@

Figure \ref{fig:subj-kappa} shows a histogram of the per subject average kappa scores using ten equal width intervals covering the $\kappa$ range between 0 and 1.  It is evident from this figure that most subjects had a $\kappa$ score between $0.2-0.5$ with a overall majority of subjects having a $\kappa$ score between $0.3-0.4$. A $\kappa$ score between $0.3-0.4$ would be considered as indicating poor to fair agreement, i.e. there was some agreement between subjects but less that would be expected. However, this calculation was done across all the stimuli and as we have already mentioned some of the stimuli were deliberately designed to be non-prototypical, in particular we expected the classroom stimuli where the chairs were arranged in a circle (Figure \ref{fig:classroom-a}) and in a U shaped pattern (Figure \ref{fig:classroom-c} and its horizontally flipped equivalent) to be relatively novel situations for the subjects. Indeed, if we look at the histogram of the average pairwise $\kappa$ scores by stimuli, Figure \ref{fig:stim-kappa}, it is evident that there is a large variation, ranging from $0$ to $0.8$, in $\kappa$ scores for each stimuli.

@@

In more detail, Table \ref{tab:stimuli-kappa-scores} lists the average pairwise $\kappa$ score for each of the visual stimuli used in the experiment and the number of no region responses for each stimuli. It is clear from this table that the non-prototypical stimuli have the lowest $\kappa$ scores and also that there is relationship between typicality and the number of no region responses. Given this relatively large variation across stimuli, which we attribute to the prototypicality of the depicted situation, we computed the average pairwise $\kappa$ scores for each subject when the non-prototypical stimuli trials were excluded. Figure \ref{fig:subj-kappa-proto} presents the histogram of the resulting average pairwise subject  $\kappa$ scores by subject. Not surpringly, with the exclusion on the non-prototypical stimuli the average pairwise $\kappa$ scores increase, with over half the subjects having an average pairwise $\kappa$ score between $0.4$ and $0.6$. $\kappa$ scores in this range can be interpreted as fair to good.

@@

The analysis of the task 1 trials indicates that, over a range of domains and spatial regions, the responses from the subjects did agree, to a good degree. Furthermore, their results support the hypothesis that the defintion of CDSRs in a given context is effected by the location and orientation of objects in the environment. For example, focusing on the classroom scenes (stimuli, $a$, $c$, $e$, and $f$) the only difference between these trials was the layout of the chairs in the room and yet there is a substantial variation across these stimuli of the agreement between subjects on the specified spatial region, namely \textit{the front of the room}. Situation $f$ resulted in an average pairwise agreement of $0.393$ and in comparision situation $a$ had an average pairwise agreement of $0.0996$.

@@

Another way of testing the relationship between the variation in context and the variation in definition of the CDSRs is to look at the differences in the ranking of the P2 point in the miliatary engagement domain between the pair of stimuli (i) and (j) and the pair of stimuli (k) and (l). In stimuli (i) the friendly tanks are positioned between the P2 point and the enemy tanks whereas in stimuli (j) the P2 point is in no-mans land. Given this change in the context one would expect a higher ranking for the P2 point in context (i) than in context (j). As the results in Table \ref{tab:point-likert-scores} show this is the case with average rating of P2  stimuli (i) being higher than that for (j). This higher rating is statiscially significant at a $95\%$ confidence level. Stimuli (k) and (l) present and analagous situation with P2 being protected by an extra turret in stimuli (l) but in no-mans land in stimuli (k). Again, the average rating of P2 for stimuli (l) is higher than that of (k), although this difference is not statistically significant. Notice, that the rating of the sweetspot for the stimuli (i) and (l) remain quite high. This would indicate that the increase in the rating of the P2 points for these stimuli results from an increase in the area of the CDSR rather than a moving of the locus of the CDSR. Overall, the analysis of the ratings of the different sweetspots across the non-flipped and flipped stimuli and the variation in the ratings of the P2 points in the military domain stimuli point to the fact that both the location and the extent of a CDSR is contextually dependent.

@@

\section{Related Work}

As the results above show, in order for an artificial cognitive system to operate successfully with humans (e.g. understanding spatially-situated task utterances), they must have access to internal models which can both represent CDSRs and recognise them in new environments. Whilst spatial reasoning has been an active topic in AI and robotics for decades, CDSRs present a new problem which requires solutions beyond the current state-of-the-art. Regions are central to QSR work~\cite{Cohn:2001}. Regions can either have crisp boundaries, usually defined by geometric shapes (e.g. the bounding boxes of visually tracked objects~\cite{SridharCohn:10}), or vague boundaries created qualitatively by multiple crisp regions (e.g. the `egg-yolk model'~\cite{Cohn96b}), or by thresholding an underlying spatially-mapped function (e.g. those created by potential fields~\cite{brenneretal07ijcai} or by Gaussian kernels~\cite{burbridge-dearden12}). The fundamental decision when creating a computational model of a CDSR is the method used to represent its boundary. Given their context-dependent nature, boundary definitions based purely on single geometric shapes seem unlikely to model the regions with sufficient accuracy. However, arbitrary boundaries can be defined using a sequence of geometric primitives (usually straight lines), as in chain codes for image region representations~\cite{Freeman:1961}.

This is an approach we followed in previous work \cite{Hawes:2012}, where we developed an approach that defined CDSRs using \textit{anchor points} \cite{DBLP:journals/jetai/KlenkFTK11} as the vertices of the region polygon. Anchor points are symbolic descriptions that link a conceptual entity (e.g., the front of a classroom) to perceived entities (e.g., the lower left extent of a desk).  Once a particular representation has been modelled in this manner, we were able to find the same type of region in previously unseen rooms using analogical transfer. An example of the representation and transfer approach is Figure \ref{fig:anchor-point-transfer}.  In the know example, a human defines the front of the classroom as a polygon consisting of four anchor points.  Analogical transfer works by aligning structured representations and transferring partially aligned statements from the known example to the new environment.  In this case, the anchor points are transferred from the group of desks in the known example to the corresponding group of desks in the new environment.

\begin{figure}
  \includegraphics[width=\columnwidth]{figures/classroom-transfer.png}
  \caption{The known example defines the front of the room with four anchor points.  By transferring the anchor points to the new environment, the system is able to ground the room's front in its perception.}
  \label{fig:anchor-point-transfer}
\end{figure}

This method satisfies our criteria for a cognitive systems solution for the following reasons: (1) the alignment process integrates spatial and semantic knowledge about the environment, (2) analogy enables transfer from a single example, (3) while untested, by linking conceptual knowledge to perception, regions defined by anchor points should support any symbolic reasoning task. Applying this model to the points and regions indicated in our experiment illustrates two limitations.  Regions do not always physically bounded by objects.  In the classroom examples, people frequently did not extend the front of the room all way into the corners.  In the safety example, people did not indicate that it was safe behind the lone turret in front of the others.  This indicates that people consider the dynamics of the situation when evaluating these terms, which is not accounted for in this model.

The use of spatial regions connected to function has been explored in other robotics work, e.g. ~\cite{Karg:2012,Fasola:2013}, but these regions are based on fields anchored at single points in the environment or on a particular object. Such fields can only vary with respect to context in terms of their size, which does not make them particularly well suited to modelling CDSRs.

\section{Discussion}

>>>>

Consider the following regions (shown in Figure \ref{fig:examples}): the front of a classroom, safety in a military engagement, or the geographical feature of a bottleneck.  To determine these regions, one must identify the physical boundaries (e.g., walls, bodies of water), the objects within the environment, their orientation and their functional use (e.g., desks oriented toward a whiteboard), and other agents' intentions and capabilities (e.g., enemy tanks can move and have a range of attack).%  Furthermore, these regions exist at different levels of spatial resolution.  Consider a neighborhood in a city, whose boundaries expand and contract over time with changes to the surrounding residents and businesses.

@@

We developed the study described below in order to examine the following questions about CDSRs:
\begin{enumerate}
	\item Given a particular context how well do people agree on the location and extent of a named CDSR?
	\item Does the orientation and location of objects (with relevant functional semantics) in a given context effect the location and extent of a named CDSR?
\end{enumerate}

Both of these research questions address the fundamental claim that CDSRs are contextually defined. Question 1 addresses this claim by examining variation in CDSR placement within different situations. In a context exhibiting clear contextual clues (e.g. determining a safe zone in a battle context where all information is known and battle formations are well-defined) one would expect high agreement in human identification of the CDSR. In a less well-defined context, one might expect little to no agreement between human communicators.  Research question 2 addresses the contextual nature of CDSRs in terms of whether or not the variation in the location and extent of a CDSR systematically follow the variations  in the given context.

@@

To examine these questions, we developed two experimental tasks:
\begin{itemize}
	\item{Task 1:} subjects were presented with a visual representation of a spatial scene plus a linguistic description containing a CDSR and were tasked with drawing a polygon on the visual stimuli such that it defined the extent of the CDSR in the scene (or stated there was no such region).
	\item{Task 2:} subjects were presented with a visual representation of a spatial scene with a marked location and an accompanying spatial description and were asked to rate how well it fit with their understanding of the CDSR on a five point likert scale.
\end{itemize}

@@

@@

The classroom stimuli consisted of pairs of floor plans and photos of classrooms with different chair configurations. For example, Figure \ref{fig:classroom-a} is a floor plan of a classroom where the chairs have been arranged in a circle and Figure \ref{fig:classroom-b} is the accompanying photo of this classroom. We developed four different classroom stimuli each with a different layout of desks: a circular layout, a U shaped layout (Figure \ref{fig:classroom-c} and Figure \ref{fig:classroom-d}), a typical row-based layout with the first row of chairs close to the expected front of the room (Figure \ref{fig:classroom-e}), and the same arrangement with the front row of chairs further away from the expected front of the room (Figure \ref{fig:classroom-f})\footnote{In the interest of saving space we do not show all the classroom photo stimuli}. To control for left-right bias effects, two versions of the U shaped layout, close rows layout and far rows layout were created by horizontally flipping the layouts. Consequently, there were seven classroom stimuli (circle, U $\times$ 2, close $\times$ 2, far $\times$ 2).  The two geographical map stimuli, Figures \ref{fig:bottleneck-a} and \ref{fig:bottleneck-b}, differed in the extent of the water.  Finally, the four military engagement stimuli, Figures \ref{fig:tanks-a}, \ref{fig:tanks-b}, \ref{fig:turrets-a}, \ref{fig:tanks-b} varied the functionality of the objects in the scene (tanks that could move versus fixed turret emplacements), the location of the objects in the scenes (were the tanks close to the bottom of the image or near the top), and the number and layout of the objects (the number and layout of the turrets were varied).

@@

@@

\subsection{Task 1 - Results}
We use two methods to analyze the results of region drawing task.  First, we use interannotator agreement for two reasons: (1) if there is fair to good overall agreement, this is evidence that people change the regions they produce based systematically with context, (2) we expect less agreement in ambiguous contexts (e.g., the circle (a) and U-shaped (c) desk arrangements as well as the turret + 1 (l) military engagement configuration).  Second, we use the extent points of the regions to assess changes between trials.  That is, as the desks are moved back from stimuli (e) to (f), we expect the maximum x-coordinate of the region to increase.

@@

We use \textbf{Cohen's kappa coefficient}, $\kappa$, to measure the agreement between two regions as follows.  We generated a set of 47,000 test points that were uniformly distributed across each stimuli and used each subject's polygon to classify the test points as being inside or outside the polygon. After classifying the test points for each subject we then computed an average pairwise kappa score for each subject with all the other subjects on a per stimuli basis. In this calculation if either of the subjects in a pair entered a no region response for a particular stimuli a $\kappa$ value of 0 was used.  $\kappa$ ranges from 0 indicating no agreement beyond chance to 1 indicating complete agreement.  Typically, scores above 0.4 are considered fair agreement and 0.75 considered excellent.

@@

%However, this calculation was done across all the stimuli and as we have already mentioned some of the stimuli were deliberately designed to be non-prototypical, in particular we expected the classroom stimuli where the chairs were arranged in a circle (Figure \ref{fig:classroom-a}) and in a U shaped pattern (Figure \ref{fig:classroom-c} and its horizontally flipped equivalent) to be relatively novel contexts for the subjects. Indeed, if we look at the histogram of the average pairwise $\kappa$ scores by stimuli, Figure \ref{fig:stim-kappa}, it is evident that there is a large variation, ranging from $0$ to $0.8$, in $\kappa$ scores for each stimuli.

@@

%\begin{table}
%\centerline{
%\begin{scriptsize}
%\begin{tabular}{l c c c c c c c c c c c c c}
%% (h) - 1_2; (g) - 1_1; (k) - 3_3; (f) - 2_4; (i) - 3_1; (e-flipped) - 2_3; (j) - 3_2; (f-flipped) - 2_5; (e) - 2_2;  (l) - 3_4;  (c) -  2_6;  (c-flipped) - 2_7;  (a) - 2_1
%Stim ID & (h) & (g) & (k) & (f) & (i) & (e-flipped) & (j) & (f-flipped) & (e) & (l) & (c) & (c-flipped) & (a)\\ 
%Average Pairwise $\kappa$ & 0.5034 & 0.4585 & 0.4548 & 0.3930 & 0.3906 & 0.3813 & 0.3787 & 0.3720 & 0.3629 & 0.3164 & 0.2438 & 0.2414 & 0.0996 \\ 
%No Region Responses & 0 & 1 & 0& 0& 0& 2&1&2& 1& 0&2&4& 10\\
%\hline
%\end{tabular}
%\end{scriptsize}
%}
%\label{tab:stimuli-kappa-scores}
%\caption{The average pairwise $\kappa$ scores, ordered in descending order from left to right, and the number of no region response by visual stimuli. The stimuli id are based on the labels in Figure \ref{exp-stimuli} with the horizontally flipped versions of stimuli indicated.}
%\end{table}

Table \ref{tab:stimuli-kappa-scores} lists the average pairwise $\kappa$ score for each of the visual stimuli used in the experiment and the number of no region responses for each stimuli.  It is clear from this table that the less common stimuli have the lowest $\kappa$ scores.  Each of the non-typical regions, the turret +1 arrangement (l), the u-shaped layouts (c and c-flpped), and the circle layout score have kappa scores of less than 0.35. Looking at the classroom results as a whole, these results support the hypothesis that the defintion of CDSRs in a given context is effected by the location and orientation of objects in the environment.  This dependence is observed by the fact that just moving the desks into a circle configuration the CDSR for the front of the room no longer exists.

%Given this relatively large variation across stimuli, which we attribute to the typicality of the depicted context, we computed the average pairwise $\kappa$ scores for each subject when the non-prototypical stimuli trials were excluded. 
%Figure \ref{fig:subj-kappa-proto} presents the histogram of the resulting average pairwise subject  $\kappa$ scores by subject. Not surpringly, with the exclusion on the non-prototypical stimuli the average pairwise $\kappa$ scores increase, with over half the subjects having an average pairwise $\kappa$ score between $0.4$ and $0.6$. $\kappa$ scores in this range can be interpreted as fair to good.

@@

%The analysis of the task 1 trials indicates that, over a range of domains and spatial regions, the responses from the subjects did agree, to a good degree. Furthermore, their results support the hypothesis that the defintion of CDSRs in a given context is effected by the location and orientation of objects in the environment. For example, focusing on the classroom scenes (stimuli, $a$, $c$, $e$, and $f$) the only difference between these trials was the layout of the chairs in the room and yet there is a substantial variation across these stimuli of the agreement between subjects on the specified spatial region, namely \textit{the front of the room}. Situation $f$ resulted in an average pairwise agreement of $0.393$ and in comparision context $a$ had an average pairwise agreement of $0.0996$.

@@

Another way of testing the relationship between the variation in context and the variation in definition of the CDSRs is to look at the differences in the ranking of the P2 point in the miliatary engagement domain between the pair of stimuli (i) and (j) and the pair of stimuli (k) and (l). In stimuli (i) the friendly tanks are positioned between the P2 point and the enemy tanks whereas in stimuli (j) the P2 point is in no-mans land. Given this change in the context one would expect a higher ranking for the P2 point in context (i) than in context (j). As the results in Table \ref{tab:point-likert-scores} show this is the case with average rating of P2  stimuli (i) being higher than that for (j). This higher rating is statiscially significant at a $95\%$ confidence level. Stimuli (k) and (l) present and analagous context with P2 being protected by an extra turret in stimuli (l) but in no-mans land in stimuli (k). Again, the average rating of P2 for stimuli (l) is higher than that of (k), although this difference is not statistically significant. Notice, that the rating of the sweetspot for the stimuli (i) and (l) remain quite high. This would indicate that the increase in the rating of the P2 points for these stimuli results from an increase in the area of the CDSR rather than a moving of the locus of the CDSR. Overall, the analysis of the ratings of the different sweetspots across the non-flipped and flipped stimuli and the variation in the ratings of the P2 points in the military domain stimuli point to the fact that both the location and the extent of a CDSR is contextually dependent.

@@

\section{Applicability of Previous Approaches to Cognitive Systems }

Recall from section \ref{} that in addition to being able to represent these regions for a single environment, the cognitive system (1) must recognize regions of the same type in new environments with new contexts, and (2) use the region for multiple reasoning tasks.  While spatial reasoning has been an active topic in AI and robotics for decades, CDSRs present a new problem which requires solutions beyond the current state-of-the-art. Regions are central to QSR work~\cite{Cohn:2001}. Regions can either have crisp boundaries, usually defined by geometric shapes (e.g. the bounding boxes of visually tracked objects~\cite{SridharCohn:10}), or vague boundaries created qualitatively by multiple crisp regions (e.g. the `egg-yolk model'~\cite{Cohn96b}), or by thresholding an underlying spatially-mapped function (e.g. those created by potential fields~\cite{brenneretal07ijcai} or by Gaussian kernels~\cite{burbridge-dearden12}). The fundamental decision when creating a computational model of a CDSR is the method used to represent its boundary. Given their context-dependent nature, boundary definitions based purely on single geometric shapes or a fixed number of points, seem unlikely to model the regions with sufficient accuracy.

However, arbitrary boundaries can be defined using a sequence of geometric primitives (usually straight lines), as in chain codes for image region representations~\cite{Freeman:1961}. This is an approach we followed in previous work \cite{Hawes:2012}, where we defined CDSRs using \textit{anchor points} \cite{DBLP:journals/jetai/KlenkFTK11} as the vertices of the region polygon thereby linking the conceptual regions to perceived objects.   While satisfying the requirements of a cognitive systems solution, applying this model to our results of our experiemnt illustrates two limitations.  First, Regions are not always physically bounded by objects.  In the classroom examples, people frequently did not extend the front of the room all way to the desks.  Second, people consider dynamics part of the context, in the safety example, people did not indicate that it was safe behind the lone turret in front of the others.

The connection between spatial regions and function has been explored in other robotics work, e.g. ~\cite{Karg:2012,Fasola:2013}, but these regions are based on fields anchored at single points in the environment or on a particular object. Therefore, they cannot account for the changes in context shown in this experiment which depend on multiple objects, agents, and simulation.

%Once a particular representation has been modelled in this manner, we were able to find the same type of region in previously unseen rooms using analogical transfer. An example of the representation and transfer approach is Figure \ref{fig:anchor-point-transfer}.  In the know example, a human defines the front of the classroom as a polygon consisting of four anchor points.  Analogical transfer works by aligning structured representations and transferring partially aligned statements from the known example to the new environment.  In this case, the anchor points are transferred from the group of desks in the known example to the corresponding group of desks in the new environment.

%\begin{figure}
%  \includegraphics[width=\columnwidth]{figures/classroom-transfer.png}
%  \caption{The known example defines the front of the room with four anchor points.  By transferring the anchor points to the new environment, the system is able to ground the room's front in its perception.}
%  \label{fig:anchor-point-transfer}
%\end{figure}

\section{Discussion}
Cognitive systems do not face problems in isolation.  Context, including its goals, objects in the environment, and other agents, impact how information is processed and how actions are undertaken.  In this paper, we presented a human study to develop requirements for reasoning about context dependent spatial regions for cognitive systems.  We found that (1) people can communicate with CDSRs, although their ability to do so decreases when situations become ambiguous, and (2) varying the location and types of the objects and agents in an environment resulted predicted changes in the location, size, and shape of the spatial region.  We outline requirements for a cognitive systems solution and discuss limitations in current approaches from cognitive systems and robotics.  Solutions to this problem will significantly improve the interaction between people and intelligent systems in human environments with applications to domestic robots, security, and activity recognition.
